Using Fundamental Measure Theory to treat the two-point pair distribution function of the Inhomogeneous Hard-Sphere Fluid

### 2013-07-02 papers/pair-correlation/paper.tex
made alterations to plot-ghs and plot-mc-mod that allow for data not being loaded properly Tested everything on node10.

\begin{align}
  g(|\rr|) = 1 + g_{sigma}e^{-x_0r} + x_1g_{sigma}sin(x_2r)e^{-x_3r} -x_4g_{sigma}^2sin(x_5r)e^(-x_6r)
\end{align}

@@

>>>>

\begin{align}
  g(|\rr|) &= 1 + g_{sigma}e^{-x_0(r-\sigma)} + x_1g_{sigma}sin(x_2(r-\sigma))e^{-x_3(r-\sigma)}\\
  &~~-x_4g_{\sigma}^2sin(x_5(r-\sigma))e^(-x_6(r-\sigma))
\end{align}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-1.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}
